\documentclass[letterpaper,12pt]{article}
\usepackage{hyperref}

\usepackage{tabularx}

%\usepackage{doublespace}
%\setstretch{1.2}

\usepackage{helvet}
\usepackage{times}
\usepackage{courier}
\usepackage{xspace}
\usepackage[T1]{fontenc}
\usepackage{mycv}
\usepackage[top=15mm,left=15mm,right=15mm,bottom=15mm]{geometry}
\begin{document}

\pagestyle{empty}

%Ueberschrift
\begin{center}
\huge{\textsc{Curriculum Vitae}}
\vspace{0.7\baselineskip}

\Large{\textsc{Masataro Asai}}
\vspace{0.5\baselineskip}

\large{
Doctoral Student

Department of General Systems Studies

Graduate School of Arts and Sciences, University of Tokyo
}

\vspace{0.8\baselineskip}

\normalsize{
 Gender: Male. Date of birth: March 28th, 1990. Present Citizenship: Japanese. \\
 Address: Saginuma-Viola 201 6-23-18 Arima Miyamae-ku Kawasaki Kanagawa, Japan. \\
 % Phone: +81-44-856-9009 \\
 Cell: +81-50-7576-3690. Email: guicho2.71828@gmail.com\ Skype: guicho2.71828\\
 Website: \url{http://guicho271828.github.io/}}
\end{center}


\section{Education}

\begin{CV}
 \item[04/2009--03/2013] B.Eng in Traffic Simulation at University of Tokyo.
 Specialization: Traffic Simulation, Multi-agent Model, Spatial Search.
 {\small Thesis: \emph{Distributed Cooperative Agents in Microscopic
 Traffic Simulation using St-RRT}; Advisor: S. Yoshimura,
 Professor. H. Fujii, Research Assistant Professor.}

 \item[04/2013--03/2015] M.A. in Artificial Intelligence at University of Tokyo.
 Specialization: Artificial Intelligence, Heuristic Search, Planning, Scheduling, Optimization
 {\small Thesis: \emph{Automated Cyclic Planning for Large Scale planning problems};
 Advisor: A. Fukunaga, Associate Professor}

 \item[04/2015--present] Continuing the study at
 University of Tokyo. {\small Advisor: A. Fukunaga, Associate Professor}
\end{CV}

\renewcommand{\refname}{Publications}

\let\uline\relax
\nocite{Asai2016}
\nocite{Asai2015}
\nocite{Asai2014}
\nocite{Asai2014b}

\bibliographystyle{plain}
\bibliography{asai-references}

\section{Professional Services}

Subreviewer for Association for Advancement of Artificial Intelligence (2015).

One of my planning domain CELL-ASSEMBLY is added to SIGAPS ``Real and
Realistic Planning Domains'' by Patrik Haslum at
\url{http://users.cecs.anu.edu.au/~patrik/sigaps/index.php?n=Main.RealDomains}
.

\section{Work Experience}

\begin{CV}

\item[12/2011--09/2012] Internship at Metamoji.inc.  Prototyped a
  drawing-chat system for iPad. Both the server and the client side are
  written in Javascript with Node.js and Titanium Mobile.

\item[04/2012--08/2012] Teaching Assistant in ``Field Work -
 Introductory Course on Automobiles'', under
 Prof.\ Kohei Kusaka.
 % The students learn the mechanism and the engineering
 % design decision of vehicles through vehicle maintenance experience.
 % prepared the maintainance materials such as lubricant, sealing and
 % oil filters, moved the vehicle which will be used for maintainance, and
 Lecture on basic safety measure and the mechanism of vehicles.
 
\item[04/2013--08/2013] Teaching Assistant in ``Experiments in
 Information and Environmental Sciences'', under
 Assoc.\ Prof.\ Haruo Saito.
 % Students are required to
 % conduct a specific experiment each week. Experiments include reading
 % the data from the various sensors and importing it to a computer,
 % during which the students are required to make use of digital circuits.
 % Tasks also include measuring the output of comparators, invert
 % amplifiers and filters that must be built by the students.
 Students have assembled and calibrated the analog or digital
 circuits to read the physical values of experimental equipments.

\item[03/2014--09/2014] Internship at LogicVein.inc,
 % LogicVein is
 a developer of a Configuration Management System
 for network routers and switches.
 % , an award-winning software that allows the users to
 % efficently manage the complex network configurations of remote routers and switches.
 % Useful batch orders can be triggered by their intuitive graphical interface.
 Worked on % . The materials
 % consist of: advertisement leaflets, blog articles and
 the technical product manual (more than 200 pages long) %  The materials
 % contain both the Japanese and English documents. Some staff are
 % native English speakers born in United States, who checked and highly
 % evaluated the quality of the English translation.
 and converted it into 
 % i also converted the Microsoft Word documents into
 % plain-text documents to set up a publishing system.  It compiles the
 % document into a \LaTeX{}-based pdf and multiple
 web pages, which is now bundled with their software.
\end{CV}

\section{Technical Skill}

\begin{CV}
 \item[Programming skill:] Familiarity with all of: 
 Object-Oriented programming,
 Functional programming,
 Logic / Rule-based programming,
 Metaprogramming and low-level optimization,
 Domain Specific Language, compile-time optimization, GPGPU.
 \item[Development skill:] Comfortable with the use of Git,
 GitHub Flow development model, Test-Driven Development, Unit
 Testing, and Continuous Integration using Travis-CI / CircleCI.
 \item[Programming Languages:]
 (professional) Common Lisp, C++, Bash, Javascript / Coffeescript, C,
 (intermediate) Java, Python,
 (elementary)   Ruby
 % \item[Hardware skill:]
 % Digital and Analog circuits, microcontrollers(Arduino,PIC), machining, welding
\end{CV}

\section{Language Ability}

\begin{CV}
 % \item[Japanese:] native
 \item[English:] TOEFL 105/120 (Reading:29/30, Listening:29/30,
 Speaking:22/30, Writing:25/30, Dec 2014). I enjoy daily discussion
 on Reddit, Github, Skype and IRC channels.
\end{CV}

\section{Community Services / Other activities}

(present) \href{https://github.com/guicho271828}{Open source activities on Github}.

(2015) \href{https://github.com/guicho271828/eazy-opencl}{eazy-opencl}
: Common Lisp interface to OpenCL 2.0 (GPGPU language similar to CUDA).

(2015) Contributer of \href{https://github.com/pocl/pocl}{POCL},
a vender-agnostic Portable OpenCL implementation in C and C++.

(2015) \href{https://github.com/guicho271828/trivia}{trivia},
\href{https://github.com/guicho271828/trivia.balland2006}{trivia.balland2006}
: An extensible and fast pattern matching compiler in Common Lisp.

(2012) Macascript : a homoiconic language that compiles into javascript.

----

(2013--present)
 Managing the TORQUE-based compute cluster (10 nodes, 80 cores) in the laboratory.
 NFS/NIS-based file system and login name synchronization.
 Secure VPN network over the campus.
 Temparature monitoring and power saving system for increased robustness.

(2011--2012) Professional mechanical engineering
 activity under project professor Kohei Kusaka (former World Rally
 Championship co-driver):
 Full engine rebuilding of 1.8L BP engine on Mazda Miata '89-'04,
 mechanical engineering(compression ratio),
 fuel map / ignition timing optimization, development of visualization
 interface \& variable resonance intake controller (Arduino).

(2011) Certification in ``basic course on machining technique'' by Prof. Ryu Chikayama.

% (2005--2007) Development of Bipedal robot with embedded microcontroller
% (Microchip\textregistered PIC and analog servo motors)


% \section{Undergraduate Thesis Abstract}
% 
% {\small
% In large-scale traffic simulation,
% microscopic multiagent model simulates the behavior of each car (an agent)
% to produce the macroscopic emergent phenomena, e.g.\  traffic-jams,
% % The accuracy of the model are validated through
% % the comparison between the k-q (traffic density to average velocity)
% % curves of simulated and actual environments.
% % which can be heavily affected by the agent behavior.
% and the development of realistic agent model is the key to maintain the simulation accuracy.
% We proposed a coorperative agent model based on Spatiotemporal RRT(St-RRT)
% and evaluated the effectiveness of our approach.
% }
% 
% \section{Masters Thesis Abstract}
% 
% {\small
% In Automated Planning \& Scheduling (P\&S),
% domains such as factory assembly requires the program to
% assemble many identical instances of a particular product.
% While modern classical
% planners can generate assembly plans for single instances of a complex
% product, generating plans to manufacture many instances of a product is
% beyond the capabilities of standard planners. We proposed ACP, a system
% which, given a model of a single instance of a product, automatically
% reformulates and solves the problem as a cyclic planning problem.  We
% showed that our ACP system can successfully generate
% cyclic plans for problems which are too large to be solved directly
% using standard planners.
% }


\end{document}
